Negative Selection in the 20th Century

### 2020-05-26 why-negative-selection.Rmd
Add regression split by household type

@@

>>>>

Lastly Figure \@ref(fig:plot-with-partner) splits respondents up by whether they
were living with a spouse or partner at the time of interview. Effects are 
generally the same sign in both groups, but are much larger among those not
living with a spouse or partner.

@@

```{r plot-with-partner, fig.cap = "Effect sizes on number of children by household type"}

drake::loadd(res_with_partner)
res_with_partner %<>% filter(grepl(":", term))

n_regs <- nrow(res_with_partner)

res_with_partner %>% 
      mutate(
        Household = ifelse(grepl("TRUE", term), "With partner", "Without partner")
      ) %>% 
      standard_ggplot(fill = Household, n_regs = n_regs, score_col = score_name)
```
